### 2015-07-08 manuscript/defs.tex
Updating defs

@@

\begin{lemma}
  Let $s$ be a seed, $r$ be a refd consistent with $s$,
  and $r'$ be an refd consistent with $s$ such that $|r'| < |r|$.  
\end{lemma}

>>>>

\begin{definition}
Given the refd $r$ of an elementary repeat family with set $S$, we say
that $r$ is {\it tight} if, for each $i$ such that $r_i = *$, there
exists two sequences defined by $S$ that have different bases in
position $i$.
\end{definition}
In other words: $r$ is tight if it only uses $*$ symbols where it must
to match everything sequence defined by $S$.

{\bf Comments:} I had it in mind that the algorithm would always
return a tight refd.  But in Carly's defense she gave the example:
s=11011, AAAAATCCCCC, AAGAATCCGCC, where ends up with AA*AA*AA*AA,
which is not tight.  Interestingly, if we have AAAAATTCCCCC and
AAGAATTCCGCC, then we get AA*AATTCC*CC -- to that extra T makes it
tight.  Not sure if this is significant.

\section{Algorithm}

Let $s$ be a fixed spaced seed, $G$ be a fixed genomic sequence, and
$f$ be a fixed integer $\geq 2$.  Let $f_s(i)$ be the sub-sequence at
$G[i]$ inducted by the seed (with 0-matching characters removed).  So $s = 11011$ and
the sequence at $G[i]$ is $AACGG$, the $f_s(i) = AAGG$.

Let $H$ and $F$ be hash-tables mapping strings to integers:
\begin{itemize}
\item $H[f(i)]$ maps reduced sequences to counts.
\item $F[f(i)]$ maps reduced sequences to family assignments.
  (e.g. $f(i)$ is assigned to family $F[f(i)]$.

Let $p(i)$ be the coorindate of $G$ the marks the beginning of the
last instance of $f(i)$.  That is, if $s=11011$ and $G =
ACCTCCAAACCTCC$, then $p(9) = 1$.  ($f(9) = CCCC$, and the largest
$i < 9$ such that $f_s(i) = CCCC$ is $i=1$.  (Not all functions are
pegged to a fixed $s$.)

\begin{verbatim}
num_fams <- 0 
for i <- 0 to |G|:
   seq = G[i:i+|s|]
   H[seq] += 1
   if H[seq] >= 2:
      pseq =

\end{verbatim}

@@
